\textbf{{\Large {Recurrent relation for branching coefficients of affine Lie algebras}}}

### 2009-11-17 AffineLieAlgebras/InformalNotes/article.tex

The paper is organised as follows. In the next subsection of the introduction we fix the notation used throughout the paper. Then in section \ref{sec:recurr-form-branch} we derive the central recurrent formula for the anomalous branching coefficients and describe the algorithm for the decomposition integrable highest weight modules of algebra $\mathfrak{g}$ to the modules of reductive subalgebra $\mathfrak{a}$ \ref{sec:algorithm}. In the next section \ref{sec:examples} we present several examples and discuss some applications in the physical models \ref{sec:phys-appl}. We conclude the paper with the review of results and the discussion of possible future developments \ref{sec:conclusion}.

@@

Consider the affine Lie algebras $\frak{g}$ and $\frak{a}$ with the
underlying finite-dimensional subalgebras $\overset{\circ }{\frak{g}}$ and $%
\overset{\circ }{\frak{a}}$ and an injection $\frak{a}\longrightarrow \frak{g%
}$ such that $\frak{a}$ is a reductive subalgebra $\frak{a\subset g}$ with
correlated root spaces: $\frak{h}_{\frak{a}}^{\ast }\subset \frak{h}_{\frak{g%
}}^{\ast }$ and $\frak{h}_{\overset{\circ }{\frak{a}}}^{\ast }\subset \frak{h%
}_{\overset{\circ }{\frak{g}}}^{\ast }$\ .

@@

\section{Recurrent formula for branching coefficients}
\label{sec:recurr-form-branch}

@@

In the next section we describe the algorithm for the computation of branching coefficients based upon this formula and then present some example and discuss physical meaning.

\subsection{Proof of the recurrent formula}
\label{sec:proof}

The decomposition of the representation of the algebra to the representations of the subalgebra can be symbolically written using formal characters and projection operator:
\begin{equation}
  \label{eq:3}
  L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}%
    }^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }\quad
  \Longrightarrow\quad
  \pi_{\mathfrak{a}}(ch L^{\mu}_{\mathfrak{g}})=\sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} ch L^{\nu}_{\mathfrak{a}}
\end{equation}
Using the Weyl-Kac formula for the character of the module
we obtain the equality
\begin{equation}
  \label{eq:4}
  \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = 
  \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu}
  \frac{\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}{\prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{\mathrm{mult}_{\mathfrak{a}}(\beta)}}
\end{equation}

It is important to mention that the projection of some of the positive roots of the algebra $\mathfrak{g}$ can be equal to zero. These roots are orthogonal to the root space of the subalgebra $\mathfrak{a}$ embedded into the root space of the algebra $\mathfrak{g}$. Let's denote the subset of these roots by $\Delta_{\bot}=\left\{\alpha\in\Delta_{\mathfrak{g}}^{+}:\forall \beta\in \Delta_{\mathfrak{a}}^{+},\; \alpha\bot\beta \right\}$.

We should notice that if the set $\Delta_{\bot}$ is non-empty than Weyl reflections which correspond to the positive roots of $\Delta_{\bot}$ generate a subgroup $W_{\bot}$ of Weyl group $W$. To prove it we should show that for any two positive roots $\alpha,\; \beta\in \Delta_{\bot}$ and corresponding Weyl reflections $\omega_{\alpha},\; \omega_{\beta}\in W_{\bot}$ there exists Weyl reflection $\omega_{\gamma}=\omega_{\alpha}\cdot \omega_{\beta}\in W_{\bot}$ and the corresponding positive root $\gamma\in \Delta_{\bot}$. Since roots of the subalgebra $\mathfrak{a}$ are invariant under $\omega_{\alpha}, \; \omega_{\beta}$ they are also invariant under the action of $\omega_{\gamma}=\omega_{\alpha}\cdot \omega_{\beta}$. Then the positive root $\gamma in \Delta^{+}$ which corresponds to $\omega_{\gamma}$ is orthogonal to the root space of $\mathfrak{a}$ and hence $\gamma\in \Delta_{\bot}$.

Since $W_{\bot}$ is the subgroup of $W$ and the space spanned over the set $\Delta_{\bot}$ is invariant under its action there exists a  subalgebra with the root space spanned over the set $\Delta_{\bot}$ which we denote by $\mathfrak{a}_{\bot}$.

Now we should discuss when the subset $\Delta_{\bot}$ is non-empty and the subgroup $W_{\bot}$ and subalgebra $\mathfrak{a}_{\bot}$ are non-trivial.

If $\mathfrak{a}$ is a maximal regular subalgebra of $\mathfrak{g}$ then rank of $\mathfrak{a}$ is equal to the rank of $\mathfrak{g}$ and it is clear that $\Delta_{\bot}$ is empty.
Then the modules $L_{\mathfrak{a}_{\bot}}$ are trivial, the dimensions are equal to 1 and we get the formula (11) from the paper \cite{ilyin812pbc}.

Non-maximal regular embedding of $\mathfrak{a}$ into $\mathfrak{g}$ can be obtained through the chain of maximal embeddings $\mathfrak{a}\subset \mathfrak{p}_1\subset \mathfrak{p}_2\subset\dots \subset \mathfrak{g}$. Also the maximal regular embeddings are constructed by the exclusion of one or two roots from the extended Dynkin diagram of the algebra. Since this process can give us non-connected Dynkin diagrams we can see which roots are orthogonal to the root space of non-maximal regular subalgebra $\mathfrak{a}$.

@@

The extended Dynkin diagram of $B_2$ 
\begin{figure}[ph]
  \centering
  \includegraphics[width=40mm]{B2_A1_diagram.pdf}
  \caption{Extended Dynkin diagram of $B_2$ and embedding of $A_1$}
  \label{fig:B2Dynkin}
\end{figure}
We then drop central node and get the embedding $A_1\oplus A_1\subset B_2$. Then $\mathfrak{a}=A_1$ and $\mathfrak{a}_{\bot}=A_1$.

In the case of special embeddings the set $\Delta_{\bot}$ can be empty as for the special embedding of $A_1\subset A_2$ with the embedding index equal to 4, or non-empty for example for the embedding $su(p)\subset su(p)\oplus su(q)\subset $
\begin{comment}
  Well, I can't understand how the roots are embedded in the special embeddings. I need some help here.
\end{comment}

@@

Since $\nu\cdot \pi_{\mathfrak{a}}(\omega(\mu+\rho))=\pi_{\mathfrak{a}}(\omega(\mu+\rho))$ and $\omega(\mu+\rho)-\pi_{\mathfrak{a}}(\omega(\mu+\rho))=\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))$, we get
\begin{multline}
  \label{eq:14}
  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \frac{\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot \omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}} =\\
  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho))-\rho} \frac{e^{\rho_{\mathfrak{a}_{\bot}} }\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot (\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}+\rho_{\mathfrak{a}_{\bot}})-\rho_{\mathfrak{a}_{\bot}}}}{\prod_{\alpha\in\Delta_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}=\\
  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho))-\rho}e^{\rho_{\mathfrak{a}_{\bot}}} ch L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}
\end{multline}
The projection $\pi_{\mathfrak{a}}$ of the character of the highest-weight module $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$ is equal to the dimension of the module multiplied by the identity element of the algebra of formal exponents. So we have
  \begin{multline}
    \label{eq:15}
    \pi_{\mathfrak{a}}\left( \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho))-\rho}e^{\rho_{\mathfrak{a}_{\bot}}} ch L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) = \\
    \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)\; \mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}
  \end{multline}
These dimensions of the modules could be easily calculated using Weyl formula.

This explicit calculation to get the character of the $\mathfrak{a}_{\bot}$ representation can be thought as the calculation of the character of the $\mathfrak{a}_{\bot}\oplus \mathfrak{h}$-module with the highest weight $\omega(\mu+\rho)$, where $\mathfrak{h}$ is the Cartan subalgebra of $\mathfrak{g}$.

@@

Let $\gamma
_{0} $ be the lowest vector with respect to the natural ordering in $%
\overset{\circ }{\Delta _{\frak{a}}}$ in the lowest grade of $\Phi _{\frak{a}\subset \frak{g}}$. Decomposing the defining relation 
\begin{equation}
  \label{eq:18}
  \prod_{\alpha\in \pi_{\mathfrak{a}}\circ (\Delta^{+}\setminus \Delta_{\bot})}\left(
    1-e^{-\alpha }\right) ^{\mathrm{{mult}\left( \alpha \right) -{mult}}_{\frak{a%
      }}\mathrm{\left( \alpha \right) }}=-s\left( \gamma _{0}\right) e^{-\gamma
    _{0}}-\sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}\setminus \left\{\gamma_{0}\right\}}s\left( \gamma \right) e^{-\gamma },  
\end{equation}
in (\ref{eq:17}) we obtain

@@

Let's describe the reduction of fundamental representation of $B_2$ with the highest weight (in fundamental weight basis) equal to $(1,0)$.
\begin{figure}[ph]
  \noindent\centering{
    \includegraphics[width=90mm]{B2_A1.pdf}
  }
  \caption{Regular embedding of $A_1$ into $B_2$}
  \label{fig:B2_A1}
\end{figure}
On the figure \ref{fig:B2_A1} we have also shown the set of points $\omega(\mu+\rho),\; \omega\in W$ of fundamental representation of $B_2$ with the corresponding determinants of Weyl reflections $\epsilon(\omega)$. 
Now we have to factorise the Weyl group $W$ by $W_{\bot}=\left\{\omega_1\right\}$. We get the following set of anomalous points $\omega(\mu+\rho)-\rho,\; \omega\in W_{\bot}\backslash W$:
\begin{figure}[ph]
  \noindent\centering{
    \includegraphics[width=90mm]{B2_A1_2.pdf}
  }
  \caption{Anomalous points and the corresponding $\mathfrak{a}_{\bot}=A_1$-modules}
  \label{fig:B2_A1_2}
\end{figure}
We have also depicted the corresponding $\mathfrak{a}_{\bot}=A_1$-modules $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$.
Then we project these points and dimensions of modules onto the root space of subalgebra $\mathfrak{a}=A_1$ and get the following anomalous points in fundamental weights basis with corresponding multiplicities:
\begin{equation}
  \label{eq:25}
  (1,2),\; (0,-3),\; (-4,3),\; (-5,-2)
\end{equation}
For the function $s(\gamma)$ and the set $\Gamma$ from the definition (\ref{phi-d},\ref{fan-defined}) we have
\begin{equation}
  \label{eq:22}
  (0,1),\; (1,2),\; (2,-1)
\end{equation}
Here the second component denotes the value of $s(\gamma)$.

Anomalous branching coefficient $k^{(1,0)}_{1}=2$, then for anomalous branching coefficient $k^{(1,0)}_{0}$ the formula (\ref{recurrent relation}) gives us
\begin{equation}
  \label{eq:23}
  k^{(1,0)}_{0}=-1\cdot k^{(1,0)}_2 +2\cdot k^{(1,0}_1 - 3\cdot \delta_{0,0} = 1
\end{equation}
So we've computed the branching coefficients.
\subsubsection{Embedding of $B_2$ into $B_4$}
\label{sec:someth-high-dimens}
Consider the the regular embedding of the subalgebra $B_2$ into the algebra $B_4$.
We calculate the branching coefficients for the fundamental representation of $B_4$.
The corresponding Dynkin diagrams are in the figure.
\begin{figure}[ph]
  \centering
  \includegraphics[width=60mm]{B4_B2_2A1.pdf}
  \caption{Dynkin diagrams}
  \label{fig:dynkin}
\end{figure}

@@

Conformal embeddings should preserve conformal invariance, so Sugawara central charge should be the same for enveloping and embedded theory.

>>>>

The paper is organised as follows. In the next subsection of the introduction we fix the notation used throughout the paper. Then in Section \ref{sec:recurr-form-branch} we derive the central recurrent formula for the anomalous branching coefficients and describe the algorithm for the decomposition of the integrable highest weight modules of algebra $\mathfrak{g}$ to the modules of a reductive subalgebra $\mathfrak{a}$ (subsection \ref{sec:algorithm}). In the next Section \ref{sec:examples} we present several examples and discuss some applications in the physical models (s. \ref{sec:phys-appl}). We conclude the paper with the review of results and discussion of possible future developments (s. \ref{sec:conclusion}).
\begin{comment}
  Fix links to the sections
\end{comment}

@@

Consider affine Lie algebras $\frak{g}$ and $\frak{a}$ with the
underlying finite-dimensional subalgebras $\overset{\circ }{\frak{g}}$ and $%
\overset{\circ }{\frak{a}}$ and an injection $\frak{a}\longrightarrow \frak{g%
}$ such that $\frak{a}$ is a reductive subalgebra $\frak{a\subset g}$ with
correlated root spaces: $\frak{h}_{\frak{a}}^{\ast }\subset \frak{h}_{\frak{g%
}}^{\ast }$ and $\frak{h}_{\overset{\circ }{\frak{a}}}^{\ast }\subset \frak{h%
}_{\overset{\circ }{\frak{g}}}^{\ast }$\ .

@@

\section{Recurrent relation for branching coefficients}
\label{sec:recurr-form-branch}

@@

In the next section we describe the algorithm for the computation of branching coefficients based upon this formula and then present some example and discuss physical meaning.
\begin{comment}
  Fix the relation so that the definitions are available for the reader.
\end{comment}
\subsection{Proof of the recurrent relation}
\label{sec:proof}

The decomposition of the representation of the algebra to the representations of the subalgebra can be symbolically written using formal characters and projection operator $\pi_{\mathfrak{a}}$ to the weight subspace:
\begin{equation}
  \label{eq:3}
  L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}%
    }^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }\quad
  \Longrightarrow\quad
  \pi_{\mathfrak{a}}(ch L^{\mu}_{\mathfrak{g}})=\sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} ch L^{\nu}_{\mathfrak{a}}
\end{equation}
Using the Weyl-Kac formula for the character of the module
we obtain the equality
\begin{equation}
  \label{eq:4}
  \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = 
  \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu}
  \frac{\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}{\prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{\mathrm{mult}_{\mathfrak{a}}(\beta)}}
\end{equation}

It is important to mention that the projection of some of the positive roots of the algebra $\mathfrak{g}$ can be equal to zero. These roots are orthogonal to the root space of the subalgebra $\mathfrak{a}$ embedded into the root space of the algebra $\mathfrak{g}$. Let's denote the subset of these roots by $\Delta_{\bot}=\left\{\alpha\in\Delta_{\mathfrak{g}}^{+}:\forall \beta\in \Delta_{\mathfrak{a}}^{+},\; \alpha\bot\beta \right\}$.
\begin{comment}
  Rewrite it: there are no roots associated with Weyl group element.

We should notice that if the set $\Delta_{\bot}$ is non-empty than Weyl reflections which correspond to the positive roots of $\Delta_{\bot}$ generate a subgroup $W_{\bot}$ of Weyl group $W$. To prove it we should show that for any two positive roots $\alpha,\; \beta\in \Delta_{\bot}$ and corresponding Weyl reflections $\omega_{\alpha},\; \omega_{\beta}\in W_{\bot}$ there exists Weyl reflection $\omega_{\gamma}=\omega_{\alpha}\cdot \omega_{\beta}\in W_{\bot}$ and the corresponding positive root $\gamma\in \Delta_{\bot}$. Since roots of the subalgebra $\mathfrak{a}$ are invariant under $\omega_{\alpha}, \; \omega_{\beta}$ they are also invariant under the action of $\omega_{\gamma}=\omega_{\alpha}\cdot \omega_{\beta}$. Then the positive root $\gamma in \Delta^{+}$ which corresponds to $\omega_{\gamma}$ is orthogonal to the root space of $\mathfrak{a}$ and hence $\gamma\in \Delta_{\bot}$. 
\end{comment}
Since $W_{\bot}$ is the subgroup of $W$ and the space spanned over the set $\Delta_{\bot}$ is invariant under its action there exists a  subalgebra with the root space spanned over the set $\Delta_{\bot}$ which we denote by $\mathfrak{a}_{\bot}$.

Now we should discuss when the subset $\Delta_{\bot}$ is non-empty and the subgroup $W_{\bot}$ and subalgebra $\mathfrak{a}_{\bot}$ are non-trivial.
\begin{comment}
  Rewrite the following paragraph so that the limit is correct. Add the formula from the paper \cite{ilyin812pbc} here or near the recurrent relation (\ref{eq:1}).
\end{comment}
If $\mathfrak{a}$ is a maximal regular subalgebra of $\mathfrak{g}$ then rank of $\mathfrak{a}$ is equal to the rank of $\mathfrak{g}$ and it is clear that $\Delta_{\bot}$ is empty.
Then the modules $L_{\mathfrak{a}_{\bot}}$ are trivial, the dimensions are equal to 1 and we get the formula (11) from the paper \cite{ilyin812pbc}.
\begin{comment}
  Analyze all the regular embeddings and show when there exist orthogonal roots 
\end{comment}
Non-maximal regular embedding of $\mathfrak{a}$ into $\mathfrak{g}$ can be obtained through the chain of maximal embeddings $\mathfrak{a}\subset \mathfrak{p}_1\subset \mathfrak{p}_2\subset\dots \subset \mathfrak{g}$. Also the maximal regular embeddings are constructed by the exclusion of one or two roots from the extended Dynkin diagram of the algebra. Since this process can give us non-connected Dynkin diagrams we can see which roots are orthogonal to the root space of non-maximal regular subalgebra $\mathfrak{a}$.

@@

The extended Dynkin diagram of $B_2$ 
\begin{figure}[ph]
  \centering
  \includegraphics[width=40mm]{B2_A1_diagram.pdf}
  \caption{Extended Dynkin diagram of $B_2$ and embedding of $A_1$}
  \label{fig:B2Dynkin}
\end{figure}
We then drop central node and get the embedding $A_1\oplus A_1\subset B_2$. Then $\mathfrak{a}=A_1$ and $\mathfrak{a}_{\bot}=A_1$.
\begin{comment}
  Add the embedding index to the definitions
\end{comment}
In the case of special embeddings the set $\Delta_{\bot}$ can be empty as for the special embedding of $A_1\subset A_2$ with the embedding index equal to 4, or non-empty for example for the embedding $su(p)\subset su(p)\oplus su(q)\subset $
\begin{comment}
  Add here the example
\end{comment}

@@

Since $\nu\cdot \pi_{\mathfrak{a}}(\omega(\mu+\rho))=\pi_{\mathfrak{a}}(\omega(\mu+\rho))$ and $\omega(\mu+\rho)-\pi_{\mathfrak{a}}(\omega(\mu+\rho))=\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))$, we get
\begin{multline}
  \label{eq:14}
  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \frac{\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot \omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}} =\\
  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho))-\rho} \frac{e^{\rho_{\mathfrak{a}_{\bot}} }\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot (\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}+\rho_{\mathfrak{a}_{\bot}})-\rho_{\mathfrak{a}_{\bot}}}}{\prod_{\alpha\in\Delta_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}=\\
  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho))-\rho}e^{\rho_{\mathfrak{a}_{\bot}}} ch L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}
\end{multline}
The projection $\pi_{\mathfrak{a}}$ of the character of the highest-weight module $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$ is equal to the dimension of the module multiplied by the unity of the algebra of formal exponents. So we have
  \begin{multline}
    \label{eq:15}
    \pi_{\mathfrak{a}}\left( \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho))-\rho}e^{\rho_{\mathfrak{a}_{\bot}}} ch L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) = \\
    \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)\; \mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}
  \end{multline}
These dimensions of the modules could be easily calculated using the Weyl formula.
\begin{comment}
  Rewrite it, so that the following paragraph begins the computation
\end{comment}
This explicit calculation to get the character of the $\mathfrak{a}_{\bot}$ representation can be thought as the calculation of the character of the $\mathfrak{a}_{\bot}\oplus \mathfrak{h}$-module with the highest weight $\omega(\mu+\rho)$, where $\mathfrak{h}$ is the Cartan subalgebra of $\mathfrak{g}$.

@@

Let $\gamma
_{0} $ be the lowest vector with respect to the natural ordering in $%
\overset{\circ }{\Delta _{\frak{a}}}$ in the lowest grade of $\Phi _{\frak{a}\subset \frak{g}}$. Decomposing the defining relation (\ref{fan-d}) 
\begin{equation}
  \label{eq:18}
  \prod_{\alpha\in \pi_{\mathfrak{a}}\circ (\Delta^{+}\setminus \Delta_{\bot})}\left(
    1-e^{-\alpha }\right) ^{\mathrm{{mult}\left( \alpha \right) -{mult}}_{\frak{a%
      }}\mathrm{\left( \alpha \right) }}=-s\left( \gamma _{0}\right) e^{-\gamma
    _{0}}-\sum_{\gamma \in \Phi _{\frak{a}\subset \frak{g}}\setminus \left\{\gamma_{0}\right\}}s\left( \gamma \right) e^{-\gamma },  
\end{equation}
in (\ref{eq:17}) we obtain

@@

Let's describe the reduction of fundamental representation of $B_2$ with the highest weight (in fundamental weight basis) equal to $(1,0)$.
\begin{figure}[ph]
  \noindent\centering{
    \includegraphics[width=90mm]{B2_A1.pdf}
  }
  \caption{Regular embedding of $A_1$ into $B_2$}
  \label{fig:B2_A1}
\end{figure}
On the figure \ref{fig:B2_A1} we have also shown the set of points $\omega(\mu+\rho),\; \omega\in W$ of fundamental representation of $B_2$ with the corresponding determinants of Weyl reflections $\epsilon(\omega)$. 
Now we have to factorise the Weyl group $W$ by $W_{\bot}=\left\{\omega_1\right\}$. We get the following set of anomalous points $\omega(\mu+\rho)-\rho,\; \omega\in W_{\bot}\backslash W$:
\begin{figure}[ph]
  \noindent\centering{
    \includegraphics[width=90mm]{B2_A1_2.pdf}
  }
  \caption{Anomalous points and the corresponding $\mathfrak{a}_{\bot}=A_1$-modules}
  \label{fig:B2_A1_2}
\end{figure}
We have also depicted the corresponding $\mathfrak{a}_{\bot}=A_1$-modules $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$.
Then we project these points and dimensions of modules onto the root space of subalgebra $\mathfrak{a}=A_1$ and get the following anomalous points in fundamental weights basis with corresponding multiplicities:
\begin{equation}
  \label{eq:25}
  (1,2),\; (0,-3),\; (-4,3),\; (-5,-2)
\end{equation}
For the function $s(\gamma)$ and the set $\Gamma$ from the definition (\ref{phi-d},\ref{fan-defined}) we have
\begin{equation}
  \label{eq:22}
  (0,1),\; (1,2),\; (2,-1)
\end{equation}
Here the second component denotes the value of $s(\gamma)$.
\begin{comment}
  It seems that here $\Gamma$ should include only two points. Is it true?

  Think of the pictures more.
\end{comment}
Anomalous branching coefficient $k^{(1,0)}_{1}=2$, then for anomalous branching coefficient $k^{(1,0)}_{0}$ the formula (\ref{recurrent relation}) gives us
\begin{equation}
  \label{eq:23}
  k^{(1,0)}_{0}=-1\cdot k^{(1,0)}_2 +2\cdot k^{(1,0}_1 - 3\cdot \delta_{0,0} = 1
\end{equation}
So we've computed the branching coefficients.
\subsubsection{Embedding of $B_2$ into $B_4$}
\label{sec:someth-high-dimens}
Consider the the regular embedding of the subalgebra $B_2$ into the algebra $B_4$.
We calculate the branching coefficients for the fundamental representation of $B_4$.
The corresponding Dynkin diagrams are in the figure.
\begin{figure}[ph]
  \centering
  \includegraphics[width=60mm]{B4_B2_2A1.pdf}
  \caption{Dynkin diagrams}
  \label{fig:dynkin}
\end{figure}

@@

\begin{comment}
  Change ``enveloping'' into something better.
\end{comment}
Conformal embeddings should preserve conformal invariance, so Sugawara central charge should be the same for enveloping and embedded theory.
